Constrained Optimization-Based Neuro-Adaptive Control (CONAC) for Euler-Lagrange Systems Under Weight and Input Constraints

### 2025-05-02 manuscript.tex
DH's comment remove

To validate the effectiveness of the proposed CONAC, a real-time experiment was conducted on a two-link manipulator, as shown in Fig.~\ref{fig:ctrl:exp:set}. 
The OpenCR1.0 board \cite{opencr} with a 32-bit ARM Cortex and a 216 MHz clock frequency was used for the real-time implementation.
\DHHO{
The experimental setup consisted of a two-link manipulator actuated by two Cubemars AK10-90 servo motors. 
The servos were controlled using the OpenCR1.0 board which transmits the reference angle to the servos via controller area network (CAN) communication.
}
The system dynamics of the two-link manipulator is described in \eqref{eq:sys1}, the estimated system parameters are provided in Table~\ref{table:system:params}.

>>>>

To validate the effectiveness of the proposed CONAC, a real-time experiment was conducted on a two-link manipulator, as shown in Fig.~\ref{fig:ctrl:exp:set}. 
The OpenCR1.0 board \cite{opencr} with a 32-bit ARM Cortex and a 216 MHz clock frequency was used for the real-time implementation.
The two-link manipulator actuated by two Cubemars AK10-90 servo motors. 
The servos were controlled using the OpenCR1.0 board which transmits the reference angle to the servos via controller area network (CAN) communication.
The system dynamics of the two-link manipulator is described in \eqref{eq:sys1}, the estimated system parameters are provided in Table~\ref{table:system:params}.
